Results

### 2025-04-21 notebooks/00_index.qmd
feat: more features processing

```{julia}
tmin_psp = DateTime("2021-01-14")
tmax_psp = DateTime("2021-01-21")
tmin_wind = DateTime("2021-01-15")
tmax_wind = DateTime("2021-01-23")

@@

```{julia}
using Discontinuity
tau = Second(30)
# psp_events = detect_variance(PSP.B, tmin_psp, tmax_psp, tau)
wind_events = ids_finder(Wind.B, tmin_wind, tmax_wind, tau)
# thm_events = detect_variance(Wind.B, tmin_wind, tmax_wind, tau; split=Day(1))
```

@@

function make_mva_products(event, B, V, n=nothing, T3=nothing)
    B_mva = make_mva_product(event, B, B; labels=B_mva_labels, ylabel=B_ylabel)
    V_mva = make_mva_product(event, V, B; labels=V_mva_labels, ylabel=V_ylabel)
    J = Product((V_mva, B_mva), j_transform)
    result = [tnorm_combine ∘ B, V, B_mva, set(tsubtract ∘ V_mva; ylabel=ΔV_ylabel), J]
    isnothing(n) || push!(result, set(
        tsubtract ∘ Product((B_mva, n), alfven_velocity_ts);
        ylabel=ΔV_ylabel, labels=["Va_L", "Va_M", "Va_N"]
    ))
    isnothing(T3) || begin
        Λ = Product((B_mva, n, T3), anisotropy_ts; ylabel="Λ")
        Va_Λ = set(
            tsubtract ∘ Product((B_mva, n, T3), alfven_velocity_ani_ts);
            ylabel=ΔV_ylabel, labels=["Va*_L", "Va*_M", "Va*_N"]
        )
        push!(result, Λ, Va_Λ)
    end
    return result
end
```

```{julia}
tvars2_wind = [
    tnorm_combine ∘ Wind.B,
    Wind.n,
    Wind.V_GSE,
    Wind.temp,
    Wind.Temp_ani
]

@@

    wind_event = Event(wind_events, 9) # 300
    wind_T3 = extend(Wind.pTemp_ani, Second(20))
    wind_tvars = make_mva_products(wind_event, Wind.B_GSE, Wind.V_GSE, Wind.n_p, wind_T3)
    wind_tvars = [wind_tvars[3:end]; Wind.Temp_ani; Wind.n; Wind.Temp]
    for p in Wind.Temp_ani
        @info "$p" data = p(wind_event)
    end
    wind_plots = plot_candidate(f, wind_event, wind_tvars, tau)
    # themis_plots = plot_candidate(f[1, 3], Event(thm_events, 3), tvars_themis2, Minute(1); link_xaxes)
    # hideydecorations!(wind_plots)
    # hideydecorations!(themis_plots)
end
```

>>>>

```{julia}
tmin_psp = DateTime("2021-01-14")
tmax_psp = DateTime("2021-01-21")
tmin_wind = DateTime("2021-01-15")
tmax_wind = DateTime("2021-01-23")
_tmax_wind = DateTime("2021-01-15T02")

@@

```{julia}
using Discontinuity: ids_finder
tau = Second(30)
# psp_events = detect_variance(PSP.B, tmin_psp, tmax_psp, tau)
wind_events = ids_finder(Wind.B_GSE, tmin_wind, tmax_wind, tau, Wind.V_GSE, Wind.n_p)
# thm_events = detect_variance(Wind.B, tmin_wind, tmax_wind, tau; split=Day(1))
```

@@

function make_mva_products(event, B, V, n=nothing, T3=nothing)
    B_mva = make_mva_product(event, B, B; labels=B_mva_labels, ylabel=B_ylabel)
    V_mva = make_mva_product(event, V, B; labels=V_mva_labels, ylabel=V_ylabel)
    J = Product((V_mva, B_mva), j_transform)
    result = [tnorm_combine ∘ B, V, tnorm_combine ∘ B_mva, set(tsubtract ∘ V_mva; ylabel=ΔV_ylabel), J]
    isnothing(n) || push!(result, set(
        tsubtract ∘ Product((B_mva, n), alfven_velocity_ts);
        ylabel=ΔV_ylabel, labels=["Va_L", "Va_M", "Va_N"]
    ))
    isnothing(T3) || begin
        Λ = Product((B_mva, n, T3), anisotropy_ts; ylabel="Λ")
        Va_Λ = set(
            tsubtract ∘ Product((B_mva, n, T3), alfven_velocity_ani_ts);
            ylabel=ΔV_ylabel, labels=["Va*_L", "Va*_M", "Va*_N"]
        )
        push!(result, Λ, Va_Λ)
    end
    return result
end
```

```{julia}
tvars2_wind = [
    tnorm_combine ∘ Wind.B,
    Wind.n,
    Wind.V_GSE,
    Wind.Temp,
    Wind.Temp_ani
]

@@

    wind_event = AniEvent(wind_events, 1) # 300
    wind_T3 = extend(Wind.pTemp_ani, Second(20))
    wind_tvars = make_mva_products(wind_event, Wind.B_GSE, Wind.V_GSE, Wind.n_p, wind_T3)
    wind_tvars = [wind_tvars[3:end]; Wind.Temp_ani; Wind.n; Wind.Temp]
    for p in Wind.Temp_ani
        @info "$p" data = p(wind_event)
    end
    wind_plots = plot_candidate(f, wind_event, wind_tvars, tau)
    # themis_plots = plot_candidate(f[1, 3], Event(thm_events, 3), tvars_themis2, Minute(1); link_xaxes)
    # hideydecorations!(wind_plots)
    # hideydecorations!(themis_plots)
end
```
